\subsection{De Sitter space \checkmark} 
	De Sitter space is a good approximation of the geometry of our universe today and in the past while inflation\footnote{inflation: a well proofed theory of exponential expansion of space and mass in the early universe}. It is a solution of the Einstein's equations with positive energy and is a submanifold of the Minkowski space.
	
%	For defining a four-dimensional de Sitter space, we have a $(3+1)$-dimensional Minkowski space, where it would be a hyperboloid with \marginpar{siehe \cite{stringtheory_revolution} S.133}
%		\begin{equation}
%			\sum_{i=1}^4 (x^i)^2 - (x^0)^2 = R^2.			
%		\end{equation}
	
	In order to understand the form of the deSitter metric, let's start with the Riemann tensor\footnote{It should be known, that in general relativity we are in a four-dimensional Riemann manifold, where the Riemann tensor gives us the curvature.} for a \todo{was meint maximally symmetric} maximally symmetric n-dimensional manifold: 
		\begin{align}
			R_{\mu \nu \lambda \xi} = \kappa (g_{\mu \lambda} g_{\nu \xi} - g_{\mu \xi} g_{\nu \lambda})
		\end{align}
	Here $\kappa$ is a measure of the curvature.\footnote{It is normalized and more specifically, it's the Ricci curvature\todo{das ist falsch!! die ricci-krümmung ist gegeben durch R_ijki, mit summenkonvention, kappa ist hier wirklich für diesen speziellen fall einer riem. mannigfaltigkeit der wert der krümmung, du setzt mit maximal symmetrisch vorraus das die krümmung diese form hat.}, but this and more information about $\kappa$ is not needed for understanding the De Sitter space.}
	
	The already known Minkowski space is a maximally symmetric spacetime with a vanishing curvature $\kappa = 0$. If the curvature is positive, which means $\kappa > 0$, then it is called De Sitter space. For building its metric, we first take the five-dimensional Minkowski space:
		\begin{align}
			\d s^2_5 = -\d u^2 + \d x^2 + \d y^2 + \d z^2 + \d w^2
		\end{align}
	And a corresponding hyperboloid:
		\begin{align}
			-u^2 + x^2 + y^2 + z^2 + w^2 = 1
		\end{align}
	We use new coordinates $\tau, \chi, \theta$ and $\phi$:
		\begin{align}
			\begin{split}
			u &= \sinh (\tau) \\
			w &= \cosh (\tau) \cos \chi \\
			x &= \cosh (\tau) \sin \chi \cos \theta \\
			y &= \cosh (\tau) \sin \chi \sin \theta \cos \phi \\
			z &= \cosh (\tau) \sin \chi \sin \theta \sin \phi
			\end{split}
		\end{align}
	So in the end the metric on the hyperboloid looks like:
		\begin{align} \label{de-sitter}
			ds^2 = -\d \tau^2 + \cosh^2(\tau) \, \d \Omega^2_3 
		\end{align}
	with $\d \Omega_3^2 = \d \chi^2 + \sin^2 \chi (\d \theta^2 + \sin^2 \theta \d \phi^2)$
	which is the metric on a three-sphere $\Sp^3$.\footnote{A $n$-sphere is a $n$-dimensional manifold in Euclidean $(n+1)$~-~dimensional space. It´s the set of vectors with norm $1$}
	
	Just for completion, a maximally symmetric spacetime with negative curvature $\kappa < 0$ is called Anti-De Sitter space (further reading: \cite{SpacetimeCarroll}).